Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2016-11-30 paper.tex
Correct some equation errors and clarify fiducial observer discussion

In practice we use two possible fiducial observers to define the momentum
decomposition via Eqn.~\ref{eqn:def_momentum}: the fluid, or comoving, observer,
$u^\alpha=dx^\alpha/ds$, and the Eulerian, or normal, observer,
$n_\alpha=-\alpha \,\partial_\alpha t$.
Here $ds$ is a differential of proper time, $t$ is coordinate time,
and $\alpha$ is lapse.
We distinguish moments computed assuming an Eulerian observer with a tilde,
e.g. $\tilde{J}$, $\tilde{H}^\mu$, $\tilde{S}^{\mu\nu}$.
Note that these three Eulerian moments are identical to the lab-frame moments
$E$, $F^\mu$, and $P^{\mu\nu}$
defined in
\cite{shib2011-truncated_moment, ocon2015-gr1d_with_nu, fouc2015-m1_nsbh}.

@@

We use the following procedure:
\begin{enumerate}
\item
  Interpolate the equilibrium neutrino chemical potential, $\mu_\nu$,
  from the simulation grid.
\item
  Interpolate $J$ and $G$ from the simulation grid and
  compute the average neutrino energy in the fluid frame
  $\langle \varepsilon \rangle \equiv J/G$.
\item
  Compute the neutrino spectral temperature
  \begin{equation}
    T_\nu = \langle \varepsilon \rangle
    \frac{\mathscr{F}_3(\mu_\nu/T)}{\mathscr{F}_2(\mu_\nu/T)},
  \end{equation}
  where $\mathscr{F}_j$ is the Fermi integral
  \begin{equation}
    \mathscr{F}_j(\eta) = \int_0^\infty dx \, x^j (1+e^{x-\eta})^{-1}.
  \end{equation}
\item
  Assume the background neutrino fields have the same total density
  as the evolved moments
  \begin{align}
    J(\varepsilon) &=
    \frac{J}{\mathscr{F}_3(\mu_\nu/T)}
    (1+\exp(\varepsilon/T_\nu-\mu_\nu/T)^{-1}, \\
    H^\mu(\varepsilon) &=
    \frac{H^\mu}{\mathscr{F}_3(\mu_\nu/T)}
    (1+\exp(\varepsilon/T_\nu-\mu_\nu/T)^{-1}.
  \end{align}
\end{enumerate}

>>>>

In practice we use two possible fiducial observers to define the momentum
decomposition via Eqn.~\ref{eqn:def_momentum}: the Eulerian,
or normal, observer, $n_\alpha=-\alpha \,\partial_\alpha t$,
and the fluid, or comoving, observer,
$u^\alpha=W(n^\alpha+v^\alpha)$.
Here $t$ is coordinate time, $\alpha$ is lapse,
$W$ is fluid Lorentz factor, and $v^\alpha$ is fluid coordinate velocity.
We distinguish moments computed assuming an Eulerian observer with a tilde,
e.g. $\tilde{J}$, $\tilde{H}^\mu$, $\tilde{S}^{\mu\nu}$.
Note that these three Eulerian moments are identical to the lab-frame moments
$E$, $F^\mu$, and $P^{\mu\nu}$
defined in
\cite{shib2011-truncated_moment, ocon2015-gr1d_with_nu, fouc2015-m1_nsbh}.

@@

We use the following procedure:
\begin{enumerate}
\item
  Interpolate the equilibrium neutrino chemical potential, $\mu_\nu$,
  from the simulation grid.
\item
  Interpolate $J$ and $G$ from the simulation grid and
  compute the average neutrino energy in the fluid frame
  $\langle \varepsilon \rangle \equiv J/G$.
\item
  Compute the neutrino spectral temperature
  \begin{equation}
    T_\nu = \langle \varepsilon \rangle
    \frac{\mathscr{F}_2(\mu_\nu/T)}{\mathscr{F}_3(\mu_\nu/T)},
  \end{equation}
  where $\mathscr{F}_j$ is the Fermi integral
  \begin{equation}
    \mathscr{F}_j(\eta) = \int_0^\infty dx \, x^j (1+e^{x-\eta})^{-1}.
  \end{equation}
\item
  Assume the background neutrino fields have the same total density
  as the evolved moments
  \begin{align}
    J(\varepsilon) &=
    J \frac{\varepsilon^3}{T_\nu^4 \,\mathscr{F}_3(\mu_\nu/T)}
    (1+\exp(\varepsilon/T_\nu-\mu_\nu/T)^{-1}, \\
    H^\mu(\varepsilon) &=
    H^\mu \frac{\varepsilon^3}{T_\nu^4\, \mathscr{F}_3(\mu_\nu/T)}
    (1+\exp(\varepsilon/T_\nu-\mu_\nu/T)^{-1}.
  \end{align}
\end{enumerate}
